Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-27 outputs/paper/paper.Rmd
Last updated, referenced updaterd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
library(modelsummary)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
```
